``Interestingness'' in Mathematical Theory Exploration

### 2019-05-22 PhDThesis/background_theoryexploration.tex
Change listing type in theoryexploration
Headingy things
Better TE intro

\subsection{Theory Exploration}
\label{sec:theoryexploration}

@@

In this work we consider the application of \emph{(automated) theory
  exploration} to generate conjectures about code. Existing tools are able to
\emph{prove} those conjectures, and hence output \emph{novel} theorems without
guidance from the user. The method of conjecture generation is a key
characteristic of any theory exploration system, although all existing
implementations rely on brute force enumeration to some degree.

@@

%%%%% THE BELOW SEEMS TO BE INTERESTINGNESS?

@@

% \begin{lstlisting}[language=ML, xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
% Inductive Nat : Set := Z : Nat
%                      | S : Nat -> Nat.

@@

% Fixpoint plus_tail (n m : Nat) := match n with
%                                       | Z    => m
%                                       | S n' => plus_tail n' (S m)
%                                   end.
% \end{lstlisting}

@@

% \begin{lstlisting}[language=ML, xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
% (* Solve equalities by beta-normalising both sides *)
% Ltac triv := try (simpl; reflexivity).

@@

%   (* Use induction hypothesis to replace plus_tail with plus *)
%   rewrite <- (IHn (S m)).
% \end{lstlisting}

@@

% \begin{lstlisting}[language=ML, xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
% IHn' : (forall x, plus n' x = plus_tail n' x) -> plus (S n') m = plus n' (S m)
% \end{lstlisting}

@@

% \begin{lstlisting}[language=ML, xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
% IHn : forall x, plus (S n') x = plus_tail (S n') x
% \end{lstlisting}

@@

% \begin{lstlisting}[language=ML, xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
% Lemma gen n m : plus (S n) m = plus n (S m).
%   induction n; triv. (* Base case is trivial *)

@@

%   (* Trivial *)
%   reflexivity.
% Defined.
% \end{lstlisting}

% \begin{lstlisting}[language=ML, xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
%   rewrite (gen n m).
%   reflexivity.
% Defined.
% \end{lstlisting}

>>>>

\section{Theory Exploration}
\label{sec:theoryexploration}

@@

In this work we consider the application of \emph{(automated) theory
  exploration} (TE) to generate conjectures about code\footnote{In principle TE
  can be used with any formal system, but appropriate methods can differ
  according to the underlying logic, etc. that is in use. We focus on Haskell
  code to anchor these variables, and to ensure our results have immediate
  utility.}. Existing tools are able to \emph{prove} those conjectures, and
hence output \emph{novel} theorems without guidance from the user. The method of
conjecture generation is a key characteristic of any theory exploration system,
although all existing implementations rely on brute force enumeration to some
degree.

@@

% TODO
%%%%% THE BELOW SEEMS TO BE INTERESTINGNESS?

@@

% \begin{coqblock}
% Inductive Nat : Set := Z : Nat
%                      | S : Nat -> Nat.

@@

% Fixpoint plus_tail (n m : Nat) := match n with
%                                       | Z    => m
%                                       | S n' => plus_tail n' (S m)
%                                   end.
% \end{coqblock}

@@

% \begin{coqblock}
% (* Solve equalities by beta-normalising both sides *)
% Ltac triv := try (simpl; reflexivity).

@@

%   (* Use induction hypothesis to replace plus_tail with plus *)
%   rewrite <- (IHn (S m)).
% \end{coqblock}

@@

% \begin{coqblock}
% IHn' : (forall x, plus n' x = plus_tail n' x) -> plus (S n') m = plus n' (S m)
% \end{coqblock}

@@

% \begin{coqblock}
% IHn : forall x, plus (S n') x = plus_tail (S n') x
% \end{coqblock}

@@

% \begin{coqblock}
% Lemma gen n m : plus (S n) m = plus n (S m).
%   induction n; triv. (* Base case is trivial *)

@@

%   (* Trivial *)
%   reflexivity.
% Defined.
% \end{coqblock}

% \begin{coqblock}
%   rewrite (gen n m).
%   reflexivity.
% Defined.
% \end{coqblock}
